Supplementary Materials from: \textit{Innovation and elaboration on the avian tree of life}; Science Advances, in review

### 2023-06-07 Manuscript/main.tex
minor updates

\textbf{Acknowledgements.}
We thank Masahito Tusboi and three other anonymous reviewers for their suggestions that greatly helped improving the manuscript.

\textbf{Author contributions.} G.H.T., A.P.B., N.C., and T. G. designed the study. J.A.B., C.R. C., E. C.H.,  and G.H.T. curated the data. T.G. analysed the data. All authors contributed to the writing of the manuscript.

>>>>

\textbf{Acknowledgements.}
We thank M. Adams, H. van Grouw and R. Prys-Jones from the Bird Group at the NHM, Tring and H. McGhie at the Manchester Museum for providing access to and expertise in the collections.
We are indebted to the volunteer citizen scientists at \url{http://www.markmybird.org} for helping to build the database of bird bill shape and contribute to our understanding of avian evolution. 
We thank Masahito Tusboi and three other anonymous reviewers for their suggestions that greatly helped improving the manuscript.

\textbf{Author contributions.} G.H.T., A.P.B., N.C., and T. G. designed the study. J.A.B., C.R.C., E.C.H., Z.K.V., and G.H.T. curated the data. T.G. analysed the data. All authors contributed to the writing of the manuscript.

### 2023-06-07 Manuscript/supplementaries.tex
minor updates

\begin{figure}[H]
\centering
   \includegraphics[width=0.9\textwidth]{Figures/correlations_fable.pdf}
\caption{Posterior distributions of the correlation between $elaboration_{species}$ and $innovation_{species}$ for each super-orders in Fig. \ref{Fig:figure_correlations}. Species' projection onto the clade-wide phylogenetic major axis of beak variation corresponds to the correlation scores in Fig. \ref{Fig:figure_correlations}A-B and species' projections onto their own super-order's phylogenetic major axis of beak variation corresponds to the correlation scores in Fig. \ref{Fig:figure_correlations}C.}
\label{Fig:fable_correlations}
\end{figure}

@@

\begin{figure}[H]
\centering
   \includegraphics[width=0.5\textwidth]{Figures/random_skewers.pdf}
\caption{Random skewers test for the differences between the super-orders (in purple) and the orders (in gold) evolutionary rate matrices against the clade-wide matrices. And, in light gold, between the orders and their super-orders evolutionary rate matrices. The different line types (dashed and full) represent respectively the 95\% and the 75\% CI distribution and the dots represent the median skewer correlation estimate. The stars denote the median p-value estimate (0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1).}
\label{/home/tguillerme/Projects/elaboration_exploration_bird_beaks/Manuscript/Figures/others/figure_phylo_spiro_dark.png
/home/tguillerme/Projects/elaboration_exploration_bird_beaks/Manuscript/Figures/others/orthogonality_results.png
/home/tguillerme/Projects/elaboration_exploration_bird_beaks/Manuscript/Figures/others/relative_EI_gg_style.png}
\end{figure}

>>>>

\begin{figure}[H]
\centering
   \includegraphics[width=0.9\textwidth]{Figures/correlations_fable.pdf}
\caption{Posterior distributions of the correlation between $elaboration_{species}$ and $innovation_{species}$ for each super-orders in Fig. \ref{Fig:figure_correlations}. Species' projection onto the clade-wide phylogenetic major axis of beak variation corresponds to the correlation scores in Fig. \ref{Fig:figure_correlations}A-B and species' projections onto their own super-order's phylogenetic major axis of beak variation corresponds to the correlation scores in Fig. \ref{Fig:figure_correlations}C.}
\label{Fig:fable_correlations_supplementary}
\end{figure}

@@

\begin{figure}[H]
\centering
   \includegraphics[width=0.5\textwidth]{Figures/random_skewers.pdf}
\caption{Random skewers test for the differences between the super-orders (in purple) and the orders (in gold) evolutionary rate matrices against the clade-wide matrices. And, in light gold, between the orders and their super-orders evolutionary rate matrices. The different line types (dashed and full) represent respectively the 95\% and the 75\% CI distribution and the dots represent the median skewer correlation estimate. The stars denote the median p-value estimate (0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1).}
\label{Fig:random_skewers}
\end{figure}
